Efficient Coalition Formation for Web Services

### 2013-03-02 papers/coalition/coalition.tex
Changes

In this scenario, there are is a community controller by a community master web sercice. The community master has a secured request rates $(R_{master})$ from users.

>>>>

In this scenario, there are is a community controller by its master web sercice. The community master has some request rate $(R_{master})$ from users. Web services need to join a community to be able to get tasks from a master web service. Each web service comes with different quality of service patameters and a throughput $(T_ws)$. Throughput is the average rate of tasks a web
